---
title: "Geospatial Analysis"
author: "Konstantinos Pasvantis"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: 'cyborg'
    orientation: columns
    source_code: embed
    vertical_layout: fill
runtime: shiny
---
# World Map Plotting
```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(bslib)
library(rsconnect)
library(prioritizr)
library(tidyverse)
library(cshapes)
library(sf)
library(shiny)
library(sfnetworks)
library(tidygraph)
library(ggraph) 
library(plotly)
cmap.2019<-cshp(date=as.Date("2019-1-1"))
validcmap.2019 <- st_make_valid(cmap.2019)

dmat <- distmatrix(as.Date("2019-1-1"), type="mindist")




capital_dataframe<- cmap.2019[,c('capname','caplong','caplat')]%>%st_drop_geometry()
capital_sf_object<-st_as_sf(x=capital_dataframe,
                 coords = c('caplong','caplat'),
                 crs='WGS84')
a2<-ggplot(data=cmap.2019)+
  geom_sf()+
  geom_sf(data=capital_sf_object,color='red',size=0.1)+
  geom_sf_text(data=capital_sf_object,aes(label=capname),size=3.5,color='blue')

map_cents=st_centroid(validcmap.2019,of_largest=TRUE,crs='WGS84')


distances_centroids_capitals<-sapply(1:length(map_cents$geometry),function(i)st_distance(map_cents$geometry[i],capital_sf_object$geometry[i]))


cents_from_caps<-cmap.2019%>%
  add_column(distances=distances_centroids_capitals)%>%
  mutate(category=case_when(distances<100000~'1',
                            distances<=300000~'2',
                            distances>300000~'3'),distances=distances/1000)%>%
  arrange(desc(distances))

a4<-ggplot(data=cents_from_caps,aes(fill=category))+geom_sf()
# Β MEROS
cmap.2019<-cshp(date=as.Date("2019-1-1"))
newcmap.2019<-cmap.2019%>%st_drop_geometry()
newcmap.2019$going_capitals=NA
prox_matrix_countries<-proximity_matrix(validcmap.2019,0)
for (i in 1:length(newcmap.2019$country_name)){
  x=c()
  for (j in 1:length(newcmap.2019$country_name)){
      if (prox_matrix_countries[i,j]==1){
        x<-append(x,newcmap.2019[j,'capname'])}
    newcmap.2019[i,'going_capitals']=tibble(list(x))
    
  }
}

distances_between_capitals=st_distance(capital_sf_object,capital_sf_object)
row.names(distances_between_capitals)<-capital_dataframe$capname
colnames(distances_between_capitals)<-capital_dataframe$capname

newcmap.2019<-newcmap.2019[,-c(1,2,3,4,5,6,8,9,10,11)]
newcmap.2019<-drop_na(newcmap.2019)
newcmap.2019<-newcmap.2019%>%unnest('going_capitals')
newcmap.2019$distances=NA
for (i in 1:length(newcmap.2019$capname)){
  newcmap.2019$distances[i]<-distances_between_capitals[newcmap.2019$capname[i],newcmap.2019$going_capitals[i]]
}

newcmap.2019<-newcmap.2019%>%mutate(distances=distances/1000)%>%rename(from=capname,to=going_capitals)

capital_graph<-as_tbl_graph(newcmap.2019)

thm <- theme_minimal() +
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank(),
    panel.grid = element_blank(),
    panel.grid.major = element_blank(),
  ) 

theme_set(thm)




capital_graph <- capital_graph%>%
  activate(nodes) %>%
  mutate(
    title = str_to_title(name),
    label = str_replace_all(title, " ", "\n")
  )

capitals <- capital_graph %>%
  activate(nodes)%>%
  pull(title)
head(capitals)

nodes_list<-capital_graph%>%activate(nodes)%>%data.frame()
names_capitals<-nodes_list$title
as.factor(names_capitals)
names_capitals_sorted<-sort(names_capitals)
```

```{r}
bslib::bs_themer()
```

Column {.sidebar}
-----------------------------------------------------------------------

This slider corresponds to Chart A.\
In this slider you pick the meters you like for this Chart.\
This plot shows the countries whose capitals intersects with another country within a radius of given meters.

```{r}
sliderInput('metres',label='Meters for buffer:',
            min=30000,max=700000,value=100000,step = 100)
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
This chart shows the capital of every country registered for the desired date.
```{r}
dateInput('date',label='Choose the desired Date',value = '2019-1-1',min='1886-1-1',max='2019-12-12')
```








Column {data-height=300}
-----------------------------------------------------------------------
### Chart A
Countries whose capitals have overlapping buffers with another country
```{r}
renderPlot({
  buffer<-st_buffer(capital_sf_object$geometry,input$metres)
  a<-lengths(st_intersects(buffer,validcmap.2019$geometry))>1

  cmap.2019<-cmap.2019%>%add_column(overlapping_buffer=a)
  cmap.2019%>%filter(overlapping_buffer==TRUE)%>%
    ggplot()+geom_sf()
})
```
### Chart B
Capitals of all countries registered for the desired date (Zoom in to check it out)
```{r}
renderPlotly({
  cmap_des<-cshp(date=as.Date(input$date))
  capital_dataframe_des<- cmap_des[,c('capname','caplong','caplat')]%>%st_drop_geometry()
  capital_sf_object_des<-st_as_sf(x=capital_dataframe_des,
                   coords = c('caplong','caplat'),
                   crs='WGS84')
  a2<-ggplot(data=cmap_des)+
    geom_sf()+
    geom_sf(data=capital_sf_object_des,color='red',size=0.1)+
    geom_sf_text(data=capital_sf_object_des,aes(label=capname),size=3.5,color='blue')
  ggplotly(a2)
})

```

# World Map Plotting pt.2

Column {.sidebar}
-----------------------------------------------------------------------
Here we can see in Chart C that every country belongs in a special category.\
A country belongs in the first category (red colour) if the distance between its capital from its centroid is lower than 100 km.\
It belongs in the second category (green colour) if the distance between its capital from its centroid is more than 100 km and lower than 300 km.\
If their distance is more than 300km, it belongs to the third category (blue colour). \
You can zoom in the map to see it better.
<br>
<br>
<br>
<br>
<br>
<br>
<br>
In this slider you can adjust the kilometers to see which countries are this far away from greece (distance between centroids).
```{r}
sliderInput('kms',label = 'Number of Kilometers: ',min=100,max=11000,value=2000,step=100)
```










Column 
-----------------------------------------------------------------------
### Chart C
Ranking of countries based on their distance between their centroids and their capitals 
```{r}
ggplotly(a4)
```


### Chart D
Nearest countries to Greece (specified by kilometers).
```{r}
renderPlot({
  km_logical<-dmat['350',]<input$kms
  greece_below_kms<-cmap.2019[km_logical,]
  ggplot(greece_below_kms)+geom_sf()
})
```




# Networks Between Capitals


Column {.sidebar}
-----------------------------------------------------------------------
Choose the layout you would like to use for this graph. Unfortunately, we designed this graph without zoom because of errors.
```{r}
selectInput("layout_opt", label = "Layout for chart E :",
            choices = c('graphopt','kk', 'linear', 'matrix','fabric','drl'), selected = 'graphopt')
```
You can also choose if you want repelled text labels for nodes or not. Aesthetically, repelled text labels are better, but we are losing many capital labels.
```{r}
selectInput("rep", label = "Repeled node labels :",
            choices = c('Yes','No'), selected = 'No')
```








Column 
-----------------------------------------------------------------------
### Chart E
Network of capitals using different layouts 
```{r}
renderPlot({
  ggraph(capital_graph,layout =input$layout_opt,circular=ifelse(input$layout_opt=='linear',TRUE,FALSE))+geom_node_point()+
  geom_edge_link(color='gray',alpha=0.3)+geom_node_text(mapping=aes(label=name,color=name),size=3,repel=ifelse(input$rep=='Yes',TRUE,FALSE))
})




```


# Shortest path between capitals 
Column {.sidebar}
-----------------------------------------------------------------------
In this section we are searching for shortest paths between connected capitals.\
You can choose the country to begin your trip and then select the desired destination.\
Chart F finds the shortest path between two capitals, if they are connected, corresponding to the minimum distance between them.\
Chart G finds the the shortest path corresponding to the smallest number of crossing capitals possible.\
In case there is no connection between the two capitals selected, the two graphs plot the entire network.
```{r}
selectInput('start',label='Select the starting capital:', choices = names_capitals_sorted, selected = 'Athens' )
```

```{r}
selectInput('end',label='Select the destination:', choices = names_capitals_sorted, selected = 'Copenhagen' )
```

Column 
-----------------------------------------------------------------------
### Chart F
Shortest Path between capitals (considering distance)
```{r}
renderPlot({
  shortest_weighted <- capital_graph %>%
  morph(to_shortest_path, which(capitals == input$start), which(capitals == input$end) , weights = distances)

shortest_weighted <- shortest_weighted%>%
  mutate(selected_node = TRUE) %>%
  activate(edges) %>%
  mutate(selected_edge = TRUE) %>%
  unmorph() 

shortest_weighted <- shortest_weighted %>%
  activate(nodes) %>%
  mutate(selected_node = ifelse(is.na(selected_node), 1.5, 2)) %>%
  activate(edges) %>%
  mutate(selected_edge = ifelse(is.na(selected_edge), 1.5, 2)) %>%
  arrange(selected_edge)



shortest_weighted %>%
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = selected_edge), color = "gray") +
  geom_node_text(aes(label = label, color =name, alpha = selected_node ), size = 3) 
})
```


Column 
-----------------------------------------------------------------------
### Chart G
Shortest Path between capitals (considering number of capitals)
```{r}
renderPlot({
  shortest_normal <- capital_graph %>%
  morph(to_shortest_path, which(capitals == input$start), which(capitals == input$end))

shortest_normal %>%
  mutate(selected_node = TRUE) %>%
  unmorph()

shortest_normal <- shortest_normal%>%
  mutate(selected_node = TRUE) %>%
  activate(edges) %>%
  mutate(selected_edge = TRUE) %>%
  unmorph() 


shortest_normal <- shortest_normal %>%
  activate(nodes) %>%
  mutate(selected_node = ifelse(is.na(selected_node), 1, 2)) %>%
  activate(edges) %>%
  mutate(selected_edge = ifelse(is.na(selected_edge), 1, 2)) %>%
  arrange(selected_edge)

shortest_normal %>%
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = selected_edge), color = "gray") +
  geom_node_text(aes(label = label, color =name, alpha = selected_node ), size = 3)
})

```









