---
title: "Music Analysis"
author: "Konstantinos Pasvantis"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: 'cyborg'
    orientation: rows
    source_code: embed
    vertical_layout: fill
runtime: shiny
---



# All around the world
```{r global, include=FALSE}
library(datasets)
library(bslib)
library(flexdashboard)
library(rsconnect)
library(prioritizr)
library(cshapes)
library(shiny)
library(sfnetworks)
library(tidygraph)
library(ggraph) 
library(plotly)
library(stringr)
library(ggmosaic)
library(splitstackshape)
library(tidyverse)
library(spData)
library(gghighlight)
library(ggtext)
library(sf)

album<-read.csv('album.csv')
album<-album%>%separate(album,c('year','title'),sep="^\\S*\\K\\s+")
album$year<-str_sub(album$year,2,-2)%>%as.numeric()
artists<-album%>%select(c(2,1))
artists<-artists%>%cSplit('genre',sep=',',direction = 'wide' )%>%select(c(1,2,3))%>%rename(primary='genre_1',secondary='genre_2')
artists<-distinct(artists,artist,.keep_all = TRUE)
album<-album%>%cSplit('genre',sep=',',direction = 'wide' )
country_names<-world$name_long%>%st_drop_geometry()
result<-data.frame(country_names, t(sapply(paste0('\\b', country_names, '\\b'), function(x) {
  tmp <- grepl(x, album$title)
  c(perc = mean(tmp) * 100, 
    Freq = sum(tmp))
})), row.names = NULL) 

world$Freq_countries=result$Freq
```

```{r}
bslib::bs_themer()
```



Column {.sidebar}
-----------------------------------------------------------------------
In this Dashboard we are presenting 3 interesting charts produced from a music dataset. \
In this tab we can see how many times a country's name is contained in an album's title. \
You can hover over each country and have a closer look at the number of albums.\
Also, you can zoom in for your own convenience. \
(Check out in how many albums 'Japan' is contained and compare this number to the rest countries of the world)


Row {data-height=100}
-----------------------------------------------------------------------
### Total Albums
```{r}
valueBox(11461,color='primary',icon = 'fa-compact-disc')
```

### Total Artists
```{r}
valueBox(3692,color='success',icon = 'fa-microphone')
```



### Different Music Genres
```{r}
valueBox(21,color='info',icon = 'fa-music')
```


Row{data-height=700}
-----------------------------------------------------------------------
### Chart A
```{r}
a1<-world%>%ggplot(aes(fill=as.factor(Freq_countries),text=paste('Album titles containing "',name_long,'" :' ,Freq_countries)))+geom_sf()+guides(fill=guide_legend(title="Albums"))+ggtitle("Countries that are contained in an album title")
ggplotly(a1,tooltip = 'text')

```


# I'm walkin on sunshine
Column {.sidebar}
-----------------------------------------------------------------------
This chart shows the best artists through the years. Pick the number you like and a bar chart containing the artists that produced the most albums from 1938 to 2020 will show up. 

```{r}
selectInput("number_of_artists", label = "Number of Top Artists",
            choices = c(10:30), selected = 20)
```




Column {data-height=300}
-----------------------------------------------------------------------
### Chart B
```{r}
renderPlot({
  top_artists_based_on_album<-album%>%
    group_by(artist)%>%
    summarise(number_of_albums=n())%>%
    arrange(-number_of_albums)%>%head(n=input$number_of_artists)
  
  
  artist_names=strsplit(top_artists_based_on_album$artist,',')
  
  top_artists_based_on_album$artist=unlist(lapply(artist_names,
                                                  function(x) paste(x[1:length(x) %% 2 == 0],
                                                                    x[1:length(x) %% 2 != 0])))
  
  top_artists_based_on_album%>%
    ggplot(aes(x=artist,y=number_of_albums,fill=artist))+
    geom_col()+
    ggtitle(paste("Top",input$number_of_artists,"Artists based on number of albums"))+
    xlab("Artist") +
    ylab("Albums")+
    theme(legend.position = "none")+
    geom_text(aes(label=number_of_albums),vjust=1.6, color="white", size=5)+
    theme(axis.text.x = element_text(angle = 45),axis.text = element_text(size=12))
    
  
}
)

```


# What is love?

Column {.sidebar}
-----------------------------------------------------------------------
Here we can see what inspires the artists to produce songs.
It seems natural to begin with the word 'Love', but if you like to, you can see some other words that makes their songs popular. \
Without further explanation, this chart shows the top 10 years with most albums containing the word you desire in their title.
```{r}
selectInput("word", label = "Defined word:",
            choices = c('World','Dream','Woman','Man','Night','Day','Time','Love','Life','Back'), selected = 'Love')
```



Column {data-height=300}
-----------------------------------------------------------------------
### Chart C

```{r}
renderPlot({
  album%>%
  filter(str_detect(title,input$word))%>%
  group_by(year)%>%
  summarise(number_of_album_containing_word=n())%>%
  arrange(-number_of_album_containing_word)%>%head(n=10)%>%
  ggplot(aes(x=reorder(year,year),y=number_of_album_containing_word,fill=as.factor(year)))+
  geom_col()+ggtitle(paste("Years with most albums containting the word",input$word))+xlab("Year") + ylab("Number of Albums") +
  theme(legend.position = "none")+
  geom_text(aes(label=number_of_album_containing_word),vjust=1.6, color="white", size=3.5)+
  theme(axis.text=element_text(size=12))
  
})
```




